SPP-Perc: Peceptron Learning Based Enhanced Signature Path Prefetcher

### 2018-12-07 results.tex
misc changes

Figure~\ref{Fig:Coverage} shows the fraction of misses in the L2 and LLC
avoided by the various prefetchers. PPF has the highest coverage of all the
prefetchers simulated. On the SPEC CPU 2017 benchmarks, PPF reduces misses by
\textbf{62.5\%} and \textbf{82.8\%} in the L2 and LLC respectively. For the
same benchmark, the next best prefetcher, DA-AMPM, covers \textbf{48.6\%} and
\textbf{72.8\%} of the misses respectively.

@@

\subsection{Multi-core Results}
\label{Results-Multi}
In this section, we demonstrate the improvement achieved by PPF for a mix of
multi-programmed workloads.\\ \\
%
\noindent \textbf{4-Core Environment:}
Figure~\ref{Fig:4Core_SPEC2017} shows a comparison of speedups obtained on
4-core mixes of a memory intensive subset SPEC CPU 2017. We plot all 4
prefetchers, normalized to the baseline. The workloads have been sorted in
increasing order of the speedup. PPF offers a speedup of \textbf{51.2\%} on
these traces, and improvement of \textbf{11.4\%} over the baseline SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.
On a different set of fully random SPEC CPU 2017 4-core mixes (not illustrated
for space reasons), PPF provides an IPC speedup of \textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.\\ \\
%
\begin{figure}[ht]
\includegraphics[width=2.75in]{8Core_SPEC2017}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}
%
\noindent \textbf{8-Core Environment:}
The sorted comparison of speedups on the memory intensive 8-core mixes is
shown in Figure~\ref{Fig:8Core_SPEC2017}. PPF improves baseline performance
by \textbf{37.6\%}, an improvement of \textbf{9.7\%} over SPP. For a random
set of SPEC CPU 2017 mixes (not illustrated for space reasons), PPF improves
performance by \textbf{23.4\%} over the baseline, corresponding to
\textbf{4.6\%} over SPP. This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.
BOP offers a better improvement than SPP for the memory intensive mixes. This
superiority can be attributed to BOP's inherent aggressive nature. DA-AMPM is
also ahead of SPP in both the mixes. Interestingly, in all these cases, PPF
consistently outperforms the best performing prefetcher.

@@

Figure~\ref{Fig:CrossVal}(a) shows the speed-up achieved by BOP, SPP and
PPF on the memory intensive subset and the full SPEC CPU 2006 suite for a
single-processor machine. 
PPF provides a speedup of \textbf{36.3\%} over the baseline on the 
memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.1\%} over SPP and
\textbf{8.44\%} over DA-AMPM and \textbf{9.93} over BOP. On the whole of 
the SPEC CPU 2006 suite, the speedup is \textbf{19.6\%}, an improvement 
of \textbf{3.33\%} over SPP.

@@

Figure~\ref{Fig:CrossVal}(b) shows the performance benefit comparison of all
the prefetch schemes on 4 different applications in the CloudSuite benchmark.
In general, these applications are prefetch agnostic. Even so, PPF manages a
\textbf{3.78\%} improvement over no prefetching, putting it ahead of the next
best prefetcher, SPP, which provides a 3.08\% speedup.

>>>>

Figure~\ref{Fig:Coverage} shows the fraction of misses in the L2 and LLC
avoided by the various prefetchers. PPF has the highest coverage of all the
prefetchers simulated. On the SPEC CPU 2017 benchmarks, PPF reduces misses by
\textbf{75.5\%} and \textbf{86.9\%} in the L2 and LLC respectively. For the
same benchmark, the next best prefetcher, DA-AMPM, covers \textbf{54.3\%} and
\textbf{78.5\%} of the misses respectively.

@@

\subsection{Multi-core Results}
\label{Results-Multi}
In this section, we demonstrate the improvement achieved by PPF for a mix of
multi-programmed workloads.\\ \\
%
\noindent \textbf{4-Core Environment:}
Figure~\ref{Fig:4Core_SPEC2017} shows a comparison of speedups obtained on
4-core mixes of a memory intensive subset SPEC CPU 2017. We plot all 4
prefetchers, normalized to the baseline. The workloads have been sorted in
increasing order of the speedup. PPF offers a speedup of \textbf{51.2\%} on
these traces, an improvement of \textbf{11.4\%} over the underlying SPP,
\textbf{9.7\%} over the next DA-AMPM, and \textbf{16.9\%} over BOP.
On a different set of fully random SPEC CPU 2017 4-core mixes (not illustrated
for space reasons), PPF provides an IPC speedup of \textbf{26.07}\% over the
baseline, which is an improvement of \textbf{5.6}\% over SPP.\\ \\
%
\begin{figure}[ht]
\includegraphics[width=2.75in]{8Core_SPEC2017}
\caption{Speedup for 8-core SPEC CPU 2017}
\label{Fig:8Core_SPEC2017}
\end{figure}
%
\noindent \textbf{8-Core Environment:}
The sorted comparison of speedups on the memory intensive 8-core mixes is
shown in Figure~\ref{Fig:8Core_SPEC2017}. PPF improves baseline performance
by \textbf{37.6\%}, an improvement of \textbf{9.7\%} over SPP. For a random
set of SPEC CPU 2017 mixes (not illustrated for space reasons), PPF improves
performance by \textbf{23.4\%} over the baseline, corresponding to
\textbf{4.6\%} over SPP. This increased improvement achieved by PPF over the
base engine SPP in a multi-core environment is expected as PPF has a very
accurate filter, it eliminates useless prefetches before they can cause
pollution in the shared LLC.
BOP offers a better improvement than SPP for the memory intensive mixes. This
superiority can be attributed to BOP's inherent aggressive nature. DA-AMPM is
also ahead of SPP in both the mixes. Interestingly, in all these cases, PPF
consistently outperforms the best performing prefetcher.

@@

Figure~\ref{Fig:CrossVal}(a) shows the performance benefit comparison of all
the prefetch schemes on 4 different applications in the CloudSuite benchmark.
In general, these applications are prefetch agnostic. Even so, PPF manages a
\textbf{3.78\%} improvement over no prefetching, putting it ahead of the next
best prefetcher, SPP, which provides a 3.08\% speedup.

Figure~\ref{Fig:CrossVal}(b) shows the speed-up achieved 
on the memory intensive subset and the full SPEC CPU 2006 suite for a
single-processor machine. 
PPF provides a speedup of \textbf{36.3\%} over the baseline on the 
memory intensive subset of SPEC CPU
2006 benchmark, giving an improvement of \textbf{6.1\%} over SPP and
\textbf{8.44\%} over DA-AMPM and \textbf{9.93} over BOP. On the whole of 
the SPEC CPU 2006 suite, the speedup is \textbf{19.6\%}, an improvement 
of \textbf{3.33\%} over SPP.

@@
